Counterexample-guided Synthesis \\ of Closed-loop Digital Control Systems

### 2016-09-24 paper/paper.tex
add figure about sampled system

\begin{equation}
\label{Eq:running-example-plant}
P\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

@@

The authors claim that this controller $C(z)$ is extremely stable for the
discrete plant model $P(z)$.  However, if implementation aspects are
considered during verification, this controller becomes unstable.

@@

%---------------------------------
\subsection{Setup}
\label{experimental-setup}
%---------------------------------

>>>>

\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

@@

The authors claim that this controller $C(z)$ is extremely stable for the
discrete plant model $G(z)$.  However, if implementation aspects are
considered during verification, this controller becomes unstable.

@@

%---------------------------------
\subsection{Description of Benchmarks}
\label{experimental-setup}
%---------------------------------

%
\begin{equation}
\label{cruise-control-g1}
G_{1}(z)=\frac{1.51z-1.3586}{z-1}.
\end{equation} 
%
\begin{equation}
\label{cruise-control-c1}
C_{1}(z)=\frac{0.0264}{z-0.998}.
\end{equation}

All experiments were conducted on an otherwise idle Intel Core i$7$-$4790$ 
CPU $3$.$60$ GHz, $16$ GB of RAM, and Linux OS.  All times given are wall 
clock time in seconds as measured by the UNIX time command.
